Why robot programming is hard

### 2013-07-19 paper.tex
Concurrency section rewrite

\documentclass[11pt,twocolumn]{article}
\usepackage{graphicx}

@@

One important use case for personal robotics will be in-home care and assistance for disabled adults. The Robots for Humanity project~\cite{rfh}, a collaboration between Willow Garage and Georgia Tech, aims to develop technology that enables persons with motor impairments to perform personal care tasks that they otherwise might not have been able to perform without assistance, such as picking up a dropped object, fetching a towel, or even scratching an itch. Its first prototypes have enabled Henry Evans, a mute quadriplegic, to act in the world for the first time since a brainstem stroke left him paralyzed. Through physical therapy, Henry has regained the ability to make limited head motions (enough to control a cursor with his gaze) and to click a button with one finger.  Using a teleop interface custom designed for him, Henry has been able to instruct Willow Garage's PR2 robots to open cabinets in his home, fetch food from the refrigerator, and even dole out candy to trick-or-treating kids on his behalf.

@@

\section{Arm complexity}

@@

Robots are complex beings full of many moving parts. For example, Willow Garage's robotic research platform, the PR-2, has two independently controlled arms, a head that can pan and tilt, a torso that can be raised and lowered, and a base that can move and turn in all directions. Each of these parts must be controlled independently in order to orchestrate a desired robotic behavior.

@@

End user programming systems have tried to simplify the problem of concurrency. One approach used is visualizing the different components on a timeline. This approach is popular with media creation tools such as Apple's GarageBand or Autodesk's 3D Studio Max. A different approach, taken by visual programming languages such as Scratch, enable programmers to define multiple blocks of code within the workspace, all of which run simultaneously and independently.

A second option for concurrency is to reduce the end user's need to write concurrent programs by defining new primitives that cover the common cases where concurrency is needed.  For example, a robot navigation algorithm may include the ability to turn the robot's head to look in the direction of motion, eliminating the need for the user to specify this complex behavior.  As another example, a two-armed robot could have both arms linked in a mirror configuration so that a command to move one arm would cause the other to mirror its motion, thus enabling the robot to pick up symmetric objects with two hands.

Even with higher-level primitives, there will still be a need for concurrent robot programming at a higher level. One form this will take is for background tasks, such as specifying that a robot should try to tidy up the room in between (or during) its other assigned chores. Supporting high level concurrency will introduce new problems, such as task prioritization (should it interrupt its task of bringing you a beer to clean up a wine spill on carpet?).

@@

We have made use of these autonomous functions to develop a system at Willow Garage called Continuous Ops that enables casual users to control our PR2 robots through a web interface (Figure~\ref{contops}). This web interface, accessible from standard laptops or tablets, provides the ability to tell a PR2 robot to unplug itself from the power supply, navigate autonomously to anywhere in the buliding, position itself in front of a table, automatically identify graspable objects on that table, and pick up an object.

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}

@@

One important use case for personal robotics will be in-home care and assistance for disabled adults. The Robots for Humanity project~\cite{rfh}, a collaboration between Willow Garage and Georgia Tech, aims to develop technology that enables persons with motor impairments to perform personal care tasks that they otherwise might not have been able to perform without assistance, such as picking up a dropped object, fetching a towel, or even scratching an itch. Its first prototypes have enabled Henry Evans, a mute quadriplegic, to act in the world for the first time since a brainstem stroke left him paralyzed. Through physical therapy, Henry has regained the ability to make limited head motions (enough to control a cursor with his gaze) and to click a button with one finger.  Using a teleop interface custom designed for him, Henry has been able to instruct Willow Garage's PR-2 robots to open cabinets in his home, fetch food from the refrigerator, and even dole out candy to trick-or-treating kids on his behalf.

@@

\section{7-DOF arms}

@@

Robots are complex beings full of many moving parts. For example, Willow Garage's robotic research platform, the PR-2, has two independently controlled 7-DOF arms, a head that can pan and tilt, a torso that can be raised and lowered, and a base that can move and turn in all directions. Each of these parts must be controlled independently in order to orchestrate a desired robotic behavior.

@@

End user programming systems have tried to simplify the problem of concurrency. One approach used is visualizing the different components on a timeline. This approach is popular with media creation tools such as Apple's GarageBand or Autodesk's 3D Studio Max. A second paradigm, taken by visual programming languages such as Scratch, makes the notion of time a global constant and runs all blocks of user code simultaneously in the virtual environment. More research is needed to discover what paradigm works best for controlling robot parts concurrently.

% A second option for concurrency is to reduce the end user's need to write concurrent programs by defining new primitives that cover the common cases where concurrency is needed.  For example, a robot navigation algorithm may include the ability to turn the robot's head to look in the direction of motion, eliminating the need for the user to specify this complex behavior.  As another example, a two-armed robot could have both arms linked in a mirror configuration so that a command to move one arm would cause the other to mirror its motion, thus enabling the robot to pick up symmetric objects with two hands.

Even if individual robot parts can be programmed to act in parallel, there will still be a need for reasoning about concurrent robot behavior at a higher level. One form this will take is for background tasks, such as specifying that a robot should try to tidy up the room in between (or during) its other assigned chores. Supporting high level concurrency will introduce new problems, such as task prioritization (should it interrupt its task of bringing you a beer to clean up a wine spill on carpet?).

@@

We have made use of these autonomous functions to develop a system at Willow Garage called Continuous Ops that enables casual users to control our PR-2 robots through a web interface (Figure~\ref{contops}). This web interface, accessible from standard laptops or tablets, provides the ability to tell a PR-2 robot to unplug itself from the power supply, navigate autonomously to anywhere in the buliding, position itself in front of a table, automatically identify graspable objects on that table, and pick up an object.
